---
title: "OffMod_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is the R file for all plots in paper "Optimisation, Potential And Sensitivity Analysis of Offshore Energy Hub".
load packages
```{r cars}
library(ggplot2)
library(cowplot)
library(egg)
library(dplyr)
library(gridExtra)
library(viridis)
library(patchwork)
library(readxl)
library(latex2exp)
library(ggsci)
library(ggrepel)
library(ggpubr)
library(gtable)
library(scales)
```

##### energy_load_supply
```{r cars}
energy_load_supply = read_xlsx("energy_load_supply.xlsx")
ggplot(data=energy_load_supply, aes(x=period))+
  geom_line(data=energy_load_supply, aes(y=power_demand, color="power demand"),size=0.3)+
    geom_line(data=energy_load_supply, aes(y=OCGT_power, color="OCGT power"),size=0.3)+
    geom_line(data=energy_load_supply, aes(y=ave_power_demand, color="ave power demand"),size=0.3,linetype = "dashed")+
      geom_line(data=energy_load_supply, aes(y=ave_OCGT_power, color="ave OCGT power"),size=0.3,linetype = "dashed")+
  facet_grid(vars(cluster), vars(slice), scales='free', margins = "am")+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=90, hjust=0.5,vjust=0.5),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
  labs(x="\n Period (hour)",y="Power (MW)")
ggsave("electricity_load_supply.pdf", width=14, units="cm")
```

```{r cars}
energy_load_supply = read_xlsx("energy_load_supply.xlsx")
ggplot(data=energy_load_supply, aes(x=period))+
  geom_line(data=energy_load_supply, aes(y=heat_demand, color="heat demand"),size=0.3)+
  geom_line(data=energy_load_supply, aes(y=OCGT_heat, color="OCGT heat"),size=0.3)+
  geom_line(data=energy_load_supply, aes(y=ave_heat_demand, color="ave heat demand"),size=0.3,linetype="dashed")+
  geom_line(data=energy_load_supply, aes(y=ave_OCGT_heat, color="ave OCGT heat"),size=0.3,linetype="dashed")+
  facet_grid(vars(cluster), vars(slice), scales='free', margins = "am")+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=90, hjust=0.5,vjust=0.5),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
  # scale_color_npg()+
  labs(x="\n Period (hour)",y="Heat (MW)")
ggsave("heat_load_supply.pdf", width=14, units="cm")
```
#### relative power demand 
```{r cars}
rel_power_demand = read_xlsx("rel_power_demand.xlsx")
ggplot(data=rel_power_demand, aes(x=cluster, y=value, fill=type)) +
    scale_y_continuous(breaks = round(seq(0, 100, by = 10),1))+
    geom_bar(stat = "identity", position="dodge") +
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"))+
  labs(x="",y="Power demand (%)")
  # scale_fill_npg()
  #  scale_color_viridis(discrete = TRUE, option = "D")+
  # scale_fill_viridis(discrete = TRUE) 
  # scale_fill_brewer(palette = "Dark2")
ggsave("rel_power_demand.pdf", width=14,height=5.5,  units="cm")
```
##### power demand absolute value stacked bar plot
```{r cars}
power_demand = read_xlsx("power_demand.xlsx")
ggplot(data=power_demand, aes(x=cluster, y=value, fill=type)) +
    # scale_y_continuous(breaks = round(seq(0, 100, by = 10),1))+
    geom_bar(position="stack",stat="identity") +
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"))+
    # scale_fill_npg()+
  # scale_fill_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Pastel1",direction=-4)+
  labs(x="",y="Power demand (GWh/yr)")
  #  scale_color_viridis(discrete = TRUE, option = "D")+
  # scale_fill_viridis(discrete = TRUE) 
  
ggsave("power_demand.pdf", width=14,height=5.5,  units="cm")
```
#### relative emission
```{r cars}
rel_emission = read_xlsx("rel_emission.xlsx")
ggplot(data=rel_emission, aes(x=cluster, y=emission)) +
    scale_y_continuous(breaks = round(seq(0, 100, by = 10),1))+
    geom_bar(stat = "identity", position="dodge") +
theme(legend.title = element_blank(),
      legend.box="vertical", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"), panel.grid.minor=element_blank())+
  labs(x=" ",y="Emission (%)")+
  scale_fill_npg()
ggsave("rel_emission_bar.pdf", width=8.9, height=5.5, units="cm")
```
##### pie plot
```{r cars}
library(ggrepel)
rel_emission = read_xlsx("rel_emission.xlsx")
rel_emission=data.frame(remission=round(rel_emission$emission/100,digits=3),rel_emission)

df2 <- rel_emission %>% 
  mutate(
    cs = rev(cumsum(rev(remission))), 
    pos = remission/2 + lead(cs, 1),
    pos = if_else(is.na(pos), remission/2, pos))

ggplot(data=rel_emission, aes(x="", y=remission,fill=cluster)) +
  geom_col(width = 1)+
     coord_polar(theta="y",start = 0 )+
  scale_fill_brewer(palette = "Pastel1",direction=-4) +
  geom_label_repel(aes(y = pos, label = percent(remission)), data = df2, size=4, show.legend = FALSE, nudge_x = 1) +
  theme_void()+
  theme(legend.title = element_blank())
ggsave("rel_emission_pie.pdf", width=9, height=5.56, units="cm")
```


##### plot of absolute emission
```{r cars}
rel_emission = read_xlsx("emission.xlsx")
ggplot(data=rel_emission, aes(x=cluster, y=emission)) +
    geom_bar(stat = "identity", position="dodge") +
theme(legend.title = element_blank(),
      legend.box="vertical", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"), panel.grid.minor=element_blank())+
  labs(x=" ",y="Emission (t)")+
  scale_fill_npg()
ggsave("emission.pdf", width=8.9, height=5.5, units="cm")
```


##### sensitivity analysis of CO_2 tax
##### emission
```{r cars}
emission = read_xlsx("co2tax_sensitivity_5000.xlsx", sheet="emission")
emission_plot=ggplot(data=emission, aes(x=co2tax))+
  geom_line(data=emission, aes(y=emission, color="OEH"),size=0.3)+
  geom_line(data=emission, aes(y=emission_nohub, color="Base"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
 ylab("Emission (Mt)")+
     xlab(TeX("$\n CO_2$ tax (EUR/t)"))
```
##### cost
```{r cars}
cost=read_xlsx("co2tax_sensitivity_5000.xlsx", sheet="cost")
cost_plot=ggplot(data=cost, aes(x=co2tax))+
  geom_line(data=cost, aes(y=cost_hub, color="OEH"),size=0.3)+
  geom_line(data=cost, aes(y=cost_nohub, color="Base"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
 ylab("Total cost (MEUR)")+
   xlab(TeX("$\n CO_2$ tax (EUR/t)"))

ggarrange(emission_plot, cost_plot,common.legend = TRUE, legend="bottom")
ggsave("co2tax_emission_cost.pdf", width=14,height=5.5,units="cm")
```
##### energy loss
```{r cars}
el = read_xlsx("co2tax_sensitivity_5000.xlsx", sheet="energy_loss")
loss=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
tax=c(rep(el$co2tax,6))
data=data.frame(loss,type,tax)

el=read_xlsx("co2tax_nohub_sensitivity_5000.xlsx", sheet="energy_loss")
loss2=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type2 = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
tax2=c(rep(el$co2tax,6))

loss3=c(loss,loss2) 
type3=c(type,type2)
tax3=c(tax,tax2)
case=c(rep("OEH", 1506), rep("Base", 1506))
data3=data.frame(loss3,type3,tax3,case)

ggplot(data=data3, aes(x=tax3, y=loss3, fill=type3), size=1)+
  geom_area()+
    facet_wrap(~case)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
  scale_fill_brewer(palette = "Dark2")+
 ylab("Energy loss (GWh)")+
     xlab(TeX("$\n CO_2$ tax (EUR/t)"))
  
ggsave("co2tax_energy_loss.pdf", width=14,height=8.6, units="cm")
```
##### technology
```{r cars}
tech2 = read_xlsx("co2tax_sensitivity_5000.xlsx", sheet="tech")
tech2$location=factor(tech2$location, levels=c("cluster1","cluster2","cluster4","cluster3","cluster5"))
ggplot(data=tech2, aes(x=co2tax))+  
    scale_x_continuous(breaks =round(seq(0, 500, by = 150),1))+
  geom_line(data=tech2, aes(y=electrolyser, color="electrolyser"),size=0.3)+
  geom_line(data=tech2, aes(y=fuel_cell, color="fuel cell"),size=0.3)+
  geom_line(data=tech2, aes(y=battery, color="battery"),size=0.3)+
  geom_line(data=tech2, aes(y=E_boiler, color="electric boiler"),size=0.3)+
  geom_line(data=tech2, aes(y=onshore_capacity, color="onshore capacity"),size=0.3)+
  geom_line(data=tech2, aes(y=solar, color="solar"),size=0.3)+
  geom_line(data=tech2, aes(y=wind, color="wind"),size=0.3)+
  geom_line(data=tech2, aes(y=hydrogen, color= "hydrogen storage"),size=0.3)+
  facet_wrap(~location, scales = "free_y")+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=0, hjust=0.5,vjust=0.5),
      strip.text = element_text(size=8),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
 ylab("Capacity (MW)")+
     xlab(TeX("$\n CO_2$ tax (EUR/t)"))
ggsave("co2tax_tech_cap.pdf", width=14, height=8.65, units="cm")
```
##### sensitivity analysis of CO2 budget
##### emission
```{r cars}
emission = read_xlsx("co2budget_sensitivity_0.xlsx", sheet="emission")
emission_plot=ggplot(data=emission, aes(x=co2budget))+
   scale_x_reverse(breaks =round(seq(0, 5.6, by = 1),1))+
  geom_line(data=emission, aes(y=emission, color="OEH"),size=0.3)+
  geom_line(data=emission, aes(y=emission_nohub, color="Base"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
 ylab("Emission (Mt)")+
     xlab(TeX("$\n CO_2$ budget (Mt/yr)"))
```
##### cost
```{r cars}
cost=read_xlsx("co2budget_sensitivity_0.xlsx", sheet="cost")
cost_plot=ggplot(data=cost, aes(x=co2budget))+
  scale_x_reverse(breaks =round(seq(0, 5.6, by = 1),1))+
  geom_line(data=cost, aes(y=cost_hub, color="OEH"),size=0.3)+
  geom_line(data=cost, aes(y=cost_nohub, color="Base"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
 ylab("Total cost (MEUR)")+
   xlab(TeX("$\n CO_2$ budget (Mt/yr)"))
ggarrange(emission_plot, cost_plot,common.legend = TRUE, legend="bottom")
ggsave("co2budget_emission_cost.pdf", width=14,height=5.5,units="cm")
```

##### energy loss
```{r cars}
el = read_xlsx("co2budget_sensitivity_0.xlsx", sheet="energy_loss")
loss=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
budget=c(rep(el$co2budget,6))
data=data.frame(loss,type,budget)

el=read_xlsx("co2budget_nohub_sensitivity_0.xlsx", sheet="energy_loss")
loss2=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type2 = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
budget2=c(rep(el$co2budget,6))

loss3=c(loss,loss2) 
type3=c(type,type2)
budget3=c(budget,budget2)
case=c(rep("OEH", 606), rep("Base", 606))
data3=data.frame(loss3,type3,budget3,case)

ggplot(data=data3, aes(x=budget3, y=loss3, fill=type3), size=1)+
  geom_area()+ scale_x_reverse(breaks =round(seq(0, 5.6, by = 1),1))+
    facet_wrap(~case)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
  scale_fill_brewer(palette = "Dark2")+
 ylab("Energy loss (GWh)")+
     xlab(TeX("$\n CO_2$ tax (EUR/t)"))
  
ggsave("co2budget_energy_loss.pdf", width=14,height=8.6, units="cm")
```
##### technology
```{r cars}
tech2 = read_xlsx("co2budget_sensitivity_0.xlsx", sheet="tech")
ggplot(data=tech2, aes(x=co2budget))+  
    # scale_x_continuous(breaks =round(seq(0, 5000, by = 500),1))+
  scale_x_reverse(breaks =round(seq(0, 5.6, by = 1),1))+
  geom_line(data=tech2, aes(y=electrolyser, color="electrolyser"),size=0.3)+
  geom_line(data=tech2, aes(y=fuel_cell, color="fuel cell"),size=0.3)+
  geom_line(data=tech2, aes(y=battery, color="battery"),size=0.3)+
  geom_line(data=tech2, aes(y=E_boiler, color="electric boiler"),size=0.3)+
  geom_line(data=tech2, aes(y=onshore_capacity, color="onshore capacity"),size=0.3)+
  geom_line(data=tech2, aes(y=solar, color="solar"),size=0.3)+
  geom_line(data=tech2, aes(y=wind, color="wind"),size=0.3)+
  geom_line(data=tech2, aes(y=hydrogen, color= "hydrogen storage"),size=0.3)+
  # scale_y_continuous(sec.axis = sec_axis(~./1,name=" Hydrogen storage capacity (t)"))+
  facet_wrap(~location)+
  # expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=0, hjust=0.5,vjust=0.5),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
 ylab("Capacity (MW)")+
     xlab(TeX("$\n CO_2$ budget (Mt/yr)"))
ggsave("co2budget_tech_cap.pdf", width=14, height=8.65, units="cm")
```
##### sensitivity analysis of abatement cost of power from shore S1
##### emission
```{r cars}
emission = read_xlsx("abatement_cost(krt_0.5E_550tax)_sensitivity_8000.xlsx", sheet="emission")
emission_plot=ggplot(data=emission, aes(x=abatementcost))+
    scale_x_reverse(breaks =round(seq(0, 120, by = 20),1))+
  geom_line(data=emission, aes(y=emission, color="OEH"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="none")+
 ylab("Emission (Mt)")+
     xlab("AAC (EUR/t)")
```
##### cost
```{r cars}
cost=read_xlsx("abatement_cost(krt_0.5E_550tax)_sensitivity_8000.xlsx", sheet="cost")
cost_plot=ggplot(data=cost, aes(x=abatementcost))+
  scale_x_reverse(breaks =round(seq(0, 120, by = 20),1))+
  geom_line(data=cost, aes(y=cost, color="OEH"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="none")+
 ylab("Total cost (MEUR)")+
   xlab("AAC (EUR/t)")
ggarrange(emission_plot, cost_plot,common.legend = TRUE, legend="none")
ggsave("abatement_krt_emission_cost_s1.pdf", width=14,height=5.5,units="cm")
```
##### energy loss
##### truncated plot (0--120)
```{r cars}
el = read_xlsx("abatement_cost(krt_0.5E_550tax)_sensitivity_8000.xlsx", sheet="energy_loss")
loss=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
abatementcost=c(rep(el$abatementcost,6))
data=data.frame(loss,type,abatementcost)
ggplot(data=data, aes(x=abatementcost, y=loss, fill=type), size=1)+
  geom_area()+
   scale_x_reverse(breaks =round(seq(0, 120, by = 20),1))+
    # facet_wrap(~case)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
  scale_fill_brewer(palette = "Dark2")+
 ylab("Energy loss (GWh)")+
     xlab("AAC (EUR/t)")
ggsave("abatement_krt_energy_loss_s1.pdf", width=14,height=8.6, units="cm")
```

##### technology
```{r cars}
tech2 = read_xlsx("abatement_cost(krt_0.5E_550tax)_sensitivity_8000.xlsx", sheet="tech")
ggplot(data=tech2, aes(x=abatementcost))+  
  scale_x_reverse(breaks =round(seq(0, 120, by = 40),1))+
  geom_line(data=tech2, aes(y=electrolyser, color="electrolyser"),size=0.3)+
  geom_line(data=tech2, aes(y=fuel_cell, color="fuel cell"),size=0.3)+
  geom_line(data=tech2, aes(y=battery, color="battery"),size=0.3)+
  geom_line(data=tech2, aes(y=E_boiler, color="electric boiler"),size=0.3)+
  geom_line(data=tech2, aes(y=onshore_capacity, color="onshore capacity"),size=0.3)+
  geom_line(data=tech2, aes(y=solar, color="solar"),size=0.3)+
  geom_line(data=tech2, aes(y=wind, color="wind"),size=0.3)+
  geom_line(data=tech2, aes(y=hydrogen, color= "hydrogen storage"),size=0.3)+
  facet_wrap(~location)+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=0, hjust=0.5,vjust=0.5),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
 ylab("Capacity (MW)")+
     xlab(TeX("AAC (EUR/t)"))
ggsave("aac_tech_cap_s1.pdf", width=14, height=8.65, units="cm")
```

##### sensitivity analysis of abatement cost of power from shore S2
##### emission
##### cost
```{r cars}
cost=read_xlsx("abatement_cost(krt_0E_2000tax)_sensitivity_8000.xlsx", sheet="cost")
ggplot(data=cost, aes(x=abatementcost))+
  scale_x_reverse(breaks =round(seq(0, 800, by = 100),1))+
  geom_line(data=cost, aes(y=cost, color="OEH"),size=0.3)+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="none")+
 ylab("Total cost (MEUR)")+
   xlab("AAC (EUR/t)")
ggsave("abatement_krt_cost_s2.pdf", width=9,height=5.5,units="cm")
```
##### energy loss
##### truncated plot (0--120)
```{r cars}
el = read_xlsx("abatement_cost(krt_0E_2000tax)_sensitivity_8000.xlsx", sheet="energy_loss")
loss=c(el$el_OCGT, el$el_l, el$el_production, el$el_energyhub, el$el_eshed, el$el_hshed)
type = c(rep("OCGT",length(el $el_l)),rep("transmission",length(el $el_l)), rep("production",length(el $el_l)),rep("energy hub",length(el $el_l)),rep("electricity generation shed",length(el $el_l)),rep("heat generation shed",length(el $el_l)))
abatementcost=c(rep(el$abatementcost,6))
data=data.frame(loss,type,abatementcost)
ggplot(data=data, aes(x=abatementcost, y=loss, fill=type), size=1)+
  geom_area()+
   scale_x_reverse(breaks =round(seq(0,800, by = 100),1))+
  expand_limits(y=0)+
theme(legend.title = element_blank(),
      legend.box="horizontal", legend.margin=margin(),
        panel.background = element_rect(fill = "white",
                                colour = "black",
                                size = 0.25),
        axis.text.x=element_text( hjust=0.5,vjust=0.5),
        panel.grid.minor = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                colour = "grey"),
      legend.position="bottom")+
  scale_fill_brewer(palette = "Dark2")+
 ylab("Energy loss (GWh)")+
     xlab("AAC (EUR/t)")
  
ggsave("abatement_krt_energy_loss_s2.pdf", width=14,height=8.6, units="cm")
```

```{r cars}
tech2 = read_xlsx("abatement_cost(krt_0E_2000tax)_sensitivity_8000.xlsx", sheet="tech")
ggplot(data=tech2, aes(x=abatementcost))+  
  scale_x_reverse(breaks =round(seq(0, 800, by = 200),1))+
  geom_line(data=tech2, aes(y=electrolyser, color="electrolyser"),size=0.3)+
  geom_line(data=tech2, aes(y=fuel_cell, color="fuel cell"),size=0.3)+
  geom_line(data=tech2, aes(y=battery, color="battery"),size=0.3)+
  geom_line(data=tech2, aes(y=E_boiler, color="electric boiler"),size=0.3)+
  geom_line(data=tech2, aes(y=onshore_capacity, color="onshore capacity"),size=0.3)+
  geom_line(data=tech2, aes(y=solar, color="solar"),size=0.3)+
  geom_line(data=tech2, aes(y=wind, color="wind"),size=0.3)+
  geom_line(data=tech2, aes(y=hydrogen, color= "hydrogen storage"),size=0.3)+
  facet_wrap(~location)+
theme(legend.title = element_blank(),
      legend.position = "bottom",
        panel.background = element_rect(
                                colour = "black",
                                size = 0.25),

        axis.text.x=element_text(angle=0, hjust=0.5,vjust=0.5),
           panel.grid.minor = element_blank(),panel.grid.major = element_line(size = 0.25,
                                colour = "white"))+
 ylab("Capacity (MW)")+
     xlab(TeX("AAC (EUR/t)"))
ggsave("aac_tech_cap_s2.pdf", width=14, height=8.65, units="cm")
```